---
title: "Shiny demo: On-demand equity trading price chart"
author: "yatinm3, 11/3/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This Shiny application displays historical stock performance for any date range in the past 10 years.
### User Instructions

1. Enter a valid US stock symbol in the box below (for example: INTC, GOOG, MSFT, AAPL, MRK, GE, ...)
2. Select the desired date range using the slider input
```{r stockplot, echo=FALSE, warning=FALSE, message=FALSE}
library(quantmod)
#library(TTR)
# Removed symbol checking
#tickList <- stockSymbols()
#checkSymbols <- function(tick) {return(length(which(tickList$Symbol == tick)))}
stock.env <- new.env()

inputPanel(
     
  textInput("symbol", label = "Enter Valid Stock Symbol: ", value="INTC", placeholder = "Ex: MSFT or GOOG or AMZN"),

  sliderInput("date_range", "Choose Date Range:", min = as.Date("2007-01-03"), max = Sys.Date(), 
               step = 1, value = c(as.Date("2007-01-03"), Sys.Date()))
)
renderPlot({
  
  getSymbols(input$symbol, src="yahoo", env = stock.env, from = as.Date(input$date_range[1]), to = as.Date(input$date_range[2]) )
  symbol.data <- get(input$symbol, envir = stock.env)
  chartSeries(symbol.data)
})
```

Using R, Shiny, Markdown and Knitr it is super simple to embed interactive graphics on a publicly hosted html page.

The entire code is less than 15 lines and available [here](http://rpubs.com/yama3/stockplotcode).

The github repository for all the associated material is available [here](https://github.com/yatinm3/ddpShinyDemo).
